Supplementary figures

### 2021-07-02 code/figure6.Rmd
Update stanfit for knn in figure 5/6. Update survmodel lower limit for ktis to 0.05

## Processing data
load("../data/survival/survmodel_effcl_knn_062521.stansave")
dfsamps <- as.data.frame(samps)
clnames = grep("effage0\\[",names(dfsamps), value=TRUE)
dfclas = dfsamps[,clnames]
dfclas = stack(dfclas)
names(dfclas) = c("value","coefname")
dfclas$class = as.factor(as.numeric(gsub("effage0\\[(.*),(.*)\\]","\\2",dfclas$coefname)))
dfclas$tiss = tisnames[as.numeric(gsub("effage0\\[(.*),(.*)\\]","\\1",dfclas$coefname))]
dfclas$class <- fct_rev(dfclas$class)

>>>>

## Processing data
load("./survival/survmodel_effcl_knn_070121.stansave")
dfsamps <- as.data.frame(samps)
clnames = grep("effage0\\[",names(dfsamps), value=TRUE)
dfclas = dfsamps[,clnames]
dfclas = stack(dfclas)
names(dfclas) = c("value","coefname")
dfclas$class = as.factor(as.numeric(gsub("effage0\\[(.*),(.*)\\]","\\2",dfclas$coefname)))
dfclas$tiss = tisnames[as.numeric(gsub("effage0\\[(.*),(.*)\\]","\\1",dfclas$coefname))]
dfclas$class <- fct_rev(dfclas$class)

### 2021-07-02 code/survival/figure5.Rmd
Update stanfit for knn in figure 5/6. Update survmodel lower limit for ktis to 0.05

load("./survmodel_effcl_knn_062821.stansave")
cancerdat = read_csv("../../data/survival/clinical_plus_cluster.csv");
cancerdat$type <- as.factor(cancerdat$type)
tisnames <- levels(cancerdat$type)
## tissue specific effective age

>>>>

load("./survmodel_effcl_knn_070121.stansave")
cancerdat = read_csv("../../data/survival/clinical_plus_cluster.csv");
cancerdat$type <- as.factor(cancerdat$type)
tisnames <- levels(cancerdat$type)
## tissue specific effective age
